### 2019-08-08 ic-journal/intro.tex
Enriched bisimulationTheory

Another benefit of the formalisation is 
that we can take advantage of results about different 
equivalences and preorders that share similar proof structures. 
Examples are: the results that rooted bisimilarity and rooted contraction are,
respectively, the coarsest congruence contained in weak bisimilarity 
and the coarsest precongruence contained in the contraction preorder; 
the result about unique solution of equations for weak bisimilarity that uses the
contraction preorder as an auxiliary relation, and other unique solution results (e.g.~%
the one for rooted in which
the auxiliary relation is rooted contraction); various forms of enhancements of the bisimulation
proof method (the `up-to' techniques).
In these cases, moving between proofs there are only a few places in
which the HOL proof scripts have to be modified.
Then the successful termination of the proof gives us a guarantee that the proof is
complete and trustworthy, eliminating the risks 
of overlooking or missing details as in \emph{paper-and-pencil} proofs.

>>>>

Another benefit of the formalisation is 
that we can take advantage of results about different 
equivalences and preorders that share similar proof structures.
%
% Examples are: the results that rooted bisimilarity and rooted contraction are,
% respectively, the coarsest congruence contained in weak bisimilarity 
% and the coarsest precongruence contained in the contraction preorder; 
% the result about unique solution of equations for weak bisimilarity that uses the
% contraction preorder as an auxiliary relation, and other unique solution results (e.g.~%
% the one for rooted in which
% the auxiliary relation is rooted contraction); various forms of enhancements of the bisimulation
% proof method (the `up-to' techniques).
%
% rephrased: (TODO: still hard to read --Chun)
\hl{Such structural simililarities can be found, for instance, in the
following cases: the proofs that rooted bisimilarity and rooted
contraction are, respectively, the coarsest congruence contained in
weak bisimilarity and the coarsest precongruence contained in the
contraction preorder; the proofs about unique solution of equations
for weak bisimilarity that uses the contraction preorder as an
auxiliary relation, and other unique solution results (e.g. the one
for rooted in which the auxiliary relation is rooted contraction); the
proofs about various forms of enhancements of the bisimulation proof
method (the `up-to' techniques).}
%
In these cases, moving between proofs there are only a few places in
which the HOL proof scripts have to be modified.
Then the successful termination of the proof gives us a guarantee that the proof is
complete and trustworthy, eliminating the risks 
of overlooking or missing details as in \emph{paper-and-pencil} proofs.
